How to obtain the redshift distribution from probabilistic redshift estimates

### 2018-07-03 research/paper/draft.tex

\newcommand{\myemail}{aimalz@nyu.edu}
\newcommand{\mathul}{\underline}
\newcommand{\chippr}{CHIPPR}
\newcommand{\nz}{$n(z)$}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{photo-$z$ PDF}

@@

\title{How to obtain the redshift distribution from probabilistic redshift 
estimates}%:\\

@@

This paper presents the Cosmological Hierarchical Inference with Probabilistic 
Photometric Redshifts (\chippr ) model as a mathematically consistent method 
for constraining \nz s using a catalog of \pzpdf s.
In Section~\ref{sec:model}, we introduce the \chippr\ formalism; in 
Section~\ref{sec:application}, we outline how to use \chippr\ to constrain \nz\ 
from a catalog of \pzpdf s; in Section~\ref{sec:limitations} we document the 
assumptions that must hold for \chippr\ to be valid.

@@

We begin by reframing the redshift distribution \nz\ from a probabilistic 
perspective.
Here we define a redshift distribution \nz\ as the normalized probability 
density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ 
\int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We may without loss of generality impose a parametrization
\begin{equation}
\label{eqn:fz}
f_{\phi}(z)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\phi$.
We believe that galaxy redshifts are indeed drawn from \nz, making it a 
probability density over redshift; this fact can also be confirmed from 
dimensional analysis of Equation \ref{eqn:nz}.
Therefore, it can be rewritten as
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \Pr(z \mid \phi)\ \equiv\ f_{\phi}(z),
\end{equation}
a probability density over redshift conditioned on the parameters defining \nz.
Note that $z_{j}$ does not depend on $z_{j'}$, a statement of the causal 
independence of galaxy redshifts from one another.

@@

\includegraphics[width=0.3\textwidth]{fig/forward_model_example.png}
    \includegraphics[width=0.3\textwidth]{fig/forward_model_example.png}
    \includegraphics[width=0.3\textwidth]{fig/forward_model_example.png}
		\caption{Show this for each individually.}
		\label{fig:mega_scatter}
	\end{center}
\end{figure*}
Tests including all three effects at the tolerance levels of LSST and at twice 
the tolerance levels of LSST are presented in Section~\ref{sec:results}.

@@

Finally, we explicitly review the assumptions made by this approach.
\begin{itemize}
  \item prior $\Pr(\phi)$
  \item implicit prior $\phi^{*}$ known
	\item \pzpdf s are accurate posteriors %draws from photo-$z$ PDFs do 
not match marginal distributions in $z_true$ vs. $z_phot$ space, i.e. toy model 
with $z_phot$ drawn from an uglier space but pdfs evaluated in lsst-limits space
	\end{itemize}

@@

\textcolor{blue}{Q: How does the result of \chippr compare to established 
estimators in terms of the accuracy of $n(z)$?\\
A: \chippr yields the best possible $n(z)$, conditional on the accuracy of the 
photo-$z$ PDFs used.}

\subsection{Idealized example}
\label{sec:idealized}

\textcolor{blue}{LSST specs: unbiased, uniform outliers, medium z-dependent 
scatter}

\begin{figure*}
	\begin{center}

\includegraphics[width=0.45\textwidth]{fig/forward_model_example.png}
		\includegraphics[width=0.45\textwidth]{fig/results_example.png}
		\caption{Show this for idealized case.}
		\label{fig:idealized}
	\end{center}
\end{figure*}

\subsection{Realistic example}
\label{sec:realistic}

\textcolor{blue}{DES(?) specs: biased to enhance true $n(z)$, systematic 
outliers, high z-dependent scatter}

\begin{figure*}
	\begin{center}

\includegraphics[width=0.45\textwidth]{fig/forward_model_example.png}
		\includegraphics[width=0.45\textwidth]{fig/results_example.png}
		\caption{Show this for realistic case.}
		\label{fig:realistic}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}

\includegraphics[width=0.45\textwidth]{fig/forward_model_example.png}
		\includegraphics[width=0.45\textwidth]{fig/results_example.png}
		\caption{Show this for mischaracterized case.}
		\label{fig:mischaracterized}
	\end{center}
\end{figure*}

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

\newcommand{\myemail}{aimalz@nyu.edu}
\newcommand{\mathul}[1]{\underline{#1}}
\newcommand{\chippr}{CHIPPR}
\newcommand{\nz}{$n(z)$}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{photo-$z$ PDF}

@@

\title{How to obtain the redshift distribution from probabilistic redshift 
estimates}

@@

@@

We begin by reframing the redshift distribution \nz\ from a probabilistic 
perspective.
Here we define a redshift distribution \nz\ as the normalized probability 
density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ 
\int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We may without loss of generality impose a parametrization
\begin{equation}
\label{eqn:fz}
f_{\phi}(z)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\phi$.
We believe that galaxy redshifts are indeed drawn from \nz, making it a 
probability density over redshift; this fact can also be confirmed from 
dimensional analysis of Equation~\ref{eqn:nz}.
Therefore, it can be rewritten as
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \Pr(z \mid \phi)\ \equiv\ f_{\phi}(z),
\end{equation}
a probability density over redshift conditioned on the parameters defining \nz.
Note that $z_{j}$ does not depend on $z_{j'}$, a statement of the causal 
independence of galaxy redshifts from one another.

@@

\includegraphics[width=0.3\textwidth]{fig/hivarsigmas_scatter.png}
    \includegraphics[width=0.3\textwidth]{fig/uouthi_scatter.png}
    \includegraphics[width=0.3\textwidth]{fig/neghivarbias_scatter.png}
		\caption{intrinsic scatter (left), uniform outliers (center), 
bias (right);
    Not sure how best to broach the subject of nonuniform outliers and bias as 
model misspecification
    }
		\label{fig:mega_scatter}
	\end{center}
\end{figure*}
Tests including all three effects at the tolerance levels of LSST are presented 
in Section~\ref{sec:results}.

@@

Finally, we explicitly review the assumptions made by this approach.
\begin{itemize}
  \item prior $\Pr(\phi)$
  \item implicit prior $\phi^{*}$ known
	\item \pzpdf s are accurate posteriors
	\end{itemize}

@@

\textcolor{blue}{Q: How does the result of \chippr\ compare to established 
estimators in terms of the accuracy of $n(z)$?\\
A: \chippr\ yields the best possible $n(z)$, conditional on the accuracy of the 
photo-$z$ PDFs used.}

\subsection{LSST Requirements}
\label{sec:lsstdemo}

\textcolor{blue}{LSST specs: biased to 0.003, 10\% uniform outliers, 
z-dependent scatter of 0.05}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{fig/lsst_scatter.png}

\includegraphics[width=0.45\textwidth]{fig/lsst_log_estimators.png}
		\caption{Using LSST numbers}
		\label{fig:lsstdemo}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{fig/wrong_scatter.png}

\includegraphics[width=0.45\textwidth]{fig/wrong_log_estimators.png}
		\caption{this is for wrong implicit prior, not bias, haven't 
done that one yet}
		\label{fig:mischaracterized}
	\end{center}
\end{figure*}

@@

\bibliographystyle{apj}
